---
output: github_document
title:  Showing how to generate cases and staff numbers
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)

```

The first step (after installing the package) is to load the library `epicaser` and the `tidyverse`

```{r,echo=T,message=FALSE}
library(epicaser)
library(tidyverse)
```


Use the function `generate_epi_cases()` to generate synthetic data for cases. Here we use the negative binomial distribution. 

```{r,echo=T}
cases <- generate_epi_cases(Poisson = FALSE,rep_fraction = .3)
cases
```

Plot the cases

```{r}
ggplot(cases,aes(x=Date,y=Cases))+
  geom_line()+
  geom_point()+
  geom_line(aes(y=Model),colour="red")+
  scale_x_date(date_breaks = "1 week", minor_breaks = "1 day",date_labels="%b %e")
```

Next, we stratify these results into age cohorts, using the default (this can be changed).

```{r}
cases_age <- generate_cohort_epi_cases(cases$Date,cases$Cases)
cases_age
```

We can display these stratified cohorts in the following chart

```{r}
cases_tidy <- cases_age |>
                pivot_longer(names_to="Age",
                             values_to="Incidence",
                             `00-19`:`100-110`)

ggplot(cases_tidy,aes(x=Date,y=Incidence,fill=Age))+
  geom_area()+ggtitle("Synthetic Data")
```

Now, we generate an epi case list. This generates outputs showing the progress as synthetic data is created for each individual. It shows the date when each individual was infected (effectively it is an epi line list, with no contact tracing information).

```{r}
epi_cases <- generate_epi_case_list(cases_age)
epi_cases
```

We can double-check the summaries to ensure they match the aggregated values. 
```{r}
# Check summaries
epi_sum <- epi_cases %>% 
            group_by(Date,CohortGroup) %>%
            summarise(Cases=n())
epi_sum
```

These summaries are plotted.

```{r}
ggplot(epi_sum,aes(x=Date,y=Cases,fill=CohortGroup))+
  geom_area()+ggtitle("Check Case List")
```

Finally, we generate the hospital synthetic data.

```{r}
hosp_cases <- generate_hospitalisation_data(epi_cases,NL=FALSE)
hosp_cases
```

We can then generate summaries and show the admissions and dishcarges on one chart

```{r}
h_adm_sum <- hosp_cases %>%
              group_by(DateAdmitted,CohortGroup) %>%
              summarise(Admissions=n())

h_dis_sum <- hosp_cases %>%
  group_by(DateDischarged,CohortGroup) %>%
  summarise(Discharges=n())

 
ggplot()+geom_area(data=h_adm_sum,mapping=aes(x=DateAdmitted,y=Admissions,fill=CohortGroup))+
  geom_area(data=h_dis_sum,mapping=aes(x=DateDischarged,y=Discharges,fill=CohortGroup))+
  xlab("Date")+ylab("Admissions and Discharges")
```


A version can also be generated in Dutch.
```{r}
hosp_cases_nl <- generate_hospitalisation_data(epi_cases,NL=TRUE)
hosp_cases_nl
```
